Pre-orders or Philanthropy: An Analysis of Altruism on Kickstarter

### 2014-12-17 AltruisticLanguage/writing/paper.tex
updated paper

\begin{table*}[t]
\centering
\scriptsize
\begin{tabular}{|*{12}{c|}}  % repeats {c|} 18 times
\hline
\multicolumn{6}{|c}{GoFundMe vs. Kickstarter} & \multicolumn{6}{|c|}{Amazon vs. Kickstarter} \\ \hline
\multicolumn{2}{|c}{Unigrams} & \multicolumn{2}{|c}{Bigrams} & \multicolumn{2}{|c}{Trigrams} & 
\multicolumn{2}{|c}{Unigrams} & \multicolumn{2}{|c}{Bigrams} & \multicolumn{2}{|c|}{Trigrams} \\ \hline 
Unigram & Z & Bigram & Z & Trigram & Z & Unigram & Z & Bigram & Z & Trigram & Z \\ \hline
the & -77.74 & of the & -42.64 & check out the & -10.43 &
project & -366.62 & thank you & -186.89 & be able to & -141.92 \\ \hline
project & -57.09 & the story & -20.99 & a series of & -9.97 &
film & -326.85 & want to & -185.62 & thank you for & -112.63 \\ \hline
film & -48.74 & the book & -20.89 & in new york & -9.90 &
help & -293.91 & to make & -168.24 & would like to & -100.47 \\ \hline
music & -43.55 & to create & -20.33 & copy of the & -9.22 &
us & -278.78 & able to & -159.11 & a part of & -94.38 \\ \hline
of & -35.23 & the game & -18.85 & be used to & -9.13 &
money & -252.97 & be able & -142.71 & in order to & -93.87 \\ \hline \hline
she & 84.92 & thank you & 41.65 & to be able & 19.55 &
university & 88.20 & variety of & 40.80 & a member of & 24.97\\ \hline
her & 91.96 & i have & 52.57 & thank you for & 20.75 &
title & 90.43 & comes with & 43.74 & member of the & 27.22 \\ \hline
family & 98.57 & to help & 55.70 & to go to & 25.35 &
author & 91.92 & available in & 43.94 & is one of & 27.58 \\ \hline
my & 114.84 & and i & 60.22 & friends and family & 27.44 &
features & 102.99 & designed to & 46.39 & a variety of & 29.95 \\ \hline
i & 136.98 & i am & 81.20 & family and friends & 31.12 &
text & 115.04 & university of & 62.84 & one of the & 30.92 \\ \hline
\end{tabular}
\caption{Summary of Bayesian analysis of language comparing Kickstarter to GoFundMe and Amazon. Negative Z-scores correspond to Kickstarter. Top ten most significant n-grams are presented.}
\label{tab:pairwise}
\end{table*}

@@

The results of these analyses are summarized in Table \ref{tab:pairwise}. In general, our model and filtration scheme succeeds in controling for topic, though some artifacts remain. For instance, a majority of the Amazon reviews in our corpus are book reviews, which potentially obscures the intersting use of n-grams like ``university of,'' ``author,'' and ``title.'' Despite these artifacts, XXXXX.

To emperically analyze these n-gram comparisons, we first rank the n-grams in each experiment by their z-scores and compute the Spearman correlation between the Kickstarter vs. Amazon and Kickstarter vs. GoFundMe analyses. The intuition behind this comparsion is as follows: if Kickstarter is more altruistic than Amazon, but less altruistic than GoFundMe, then we would expect altruistically-associated n-grams to be on opposite ends of each ranking. We compute rankings and correlation statistics for unigrams, bigrams, and trigrams seperately.

For the 3391 unigrams, we find a negative correlation as expected, but the significance of this correlation could not be verified ($\rho = -.010, p = .55$). As we extend our analysis to more complex lingustic features such as bigrams and trigrams, which are less sensitive to unfiltered topical noise and likely carry more signal regarding the use of language, the negative correlation between these two rankings becomes more clear. For the 4195 bigrams, we see a significant negative correlation ($\rho = -.038, p < .02$) and for the 898 trigrams, we see a large significant negative correlation ($\rho = -.11, p < .002$).

>>>>

\begin{table*}[t]
\centering
\scriptsize
\begin{tabular}{|*{12}{c|}}  % repeats {c|} 18 times
\hline
\multicolumn{6}{|c}{GoFundMe vs. Kickstarter} & \multicolumn{6}{|c|}{Amazon vs. Kickstarter} \\ \hline
\multicolumn{2}{|c}{Unigrams} & \multicolumn{2}{|c}{Bigrams} & \multicolumn{2}{|c}{Trigrams} & 
\multicolumn{2}{|c}{Unigrams} & \multicolumn{2}{|c}{Bigrams} & \multicolumn{2}{|c|}{Trigrams} \\ \hline 
Unigram & Z & Bigram & Z & Trigram & Z & Unigram & Z & Bigram & Z & Trigram & Z \\ \hline
the & -77.52 & of the & -42.74 & be used to & -9.05 &
we & -685.35 & will be & -367.20 & be able to & -141.92 \\\hline
of & -42.74 & to create & -20.17 & some of the & -8.26 &
i & -525.09 & we are & -256.59 & tank you for & -112.63 \\\hline
new & -26.01 & on the & -19.96 & will be a & -6.25 &
will & -514.99 & we have & -218.54 & a part of & -94.38 \\\hline
show & -25.24 & about the & -16.48 & be used for & -6.07 &
our & -501.84 & we will & -193.24 & in order to & -93.87 \\\hline
create & -23.99 & and the & -15.65 & to make the & -6.02 &
be & -356.80 & thank you & -186.89 & to make this & -92.88 \\\hline \hline

me & 80.57 & would be & 37.02 & take care of & 16.27 &
perfect & 64.77 & is the & 48.67 & the united states & 2.88 \\\hline
was & 82.01 & name is & 37.74 & to help with & 17.72 &
has & 73.00 & and is & 54.69 & is a great & 3.75\\\hline
am & 82.62 & family and & 40.60 & in need of & 19.04 &
with & 78.24 & with a & 56.31 & is one of & 27.54\\\hline
family & 98.81 & thank you & 41.80 & thank you for & 20.38 &
includes & 81.00 & has a & 56.71 & of the most & 30.88\\\hline
i & 136.42 & to help & 55.71 & friends and family & 27.25 &
easy & 82.72 & out of & 71.67 & one of the & 30.97 \\\hline
\end{tabular}
\caption{Summary of Bayesian analysis of language comparing Kickstarter to GoFundMe and Amazon. Negative Z-scores correspond to Kickstarter. Top ten most significant n-grams are presented.}
\label{tab:pairwise}
\end{table*}

@@

The results of these analyses are summarized in Table \ref{tab:pairwise}.

To emperically analyze these n-gram comparisons, we first rank the n-grams in each experiment by their z-scores and compute Kendall's tau correlation between the Kickstarter vs. Amazon and Kickstarter vs. GoFundMe analyses. The intuition behind this comparsion is as follows: if Kickstarter is more altruistic than Amazon, but less altruistic than GoFundMe, then we would expect altruistically-associated n-grams to be on opposite ends of each ranking.

For all 2077 n-grams, we observe a statistically significant negative correlation between the rankings ($\tau = -.035, p = .016$). In addition, we compute rankings and correlation statistics for our 1119 unigrams, 1101 bigrams, and trigrams seperately. As we shift our focus from unigrams ($\tau = -.024, p = .23$) to bigrams ($\tau = -.038, p = .061$) to trigrams ($\tau = -.041, p < .01$) the negative correlation between the rankings both becomes greater and more significant. This is likely because more lingustic signal can be carried by phrases of increasing length.
